ggplot and the venn diagram for the lefse bars !

### 2021-03-02 scripts/44_ggplot_venn_lefse.Rmd
this is actually pretty cool and it solves problems

res_all <- res %>% 
  set_names(res) %>% 
  map(~ read_tsv(., col_names = c('feature','xx','direction','score','pval')) %>% 
        filter(!is.na(score))) %>% 
  keep(~ nrow(.) > 0) %>% 
  bind_rows(.id = 'res') %>% 
  mutate(tbl = if_else(str_detect(res, 'pcts'), 'pathway', if_else(str_detect(res, 'kocts'), 'KO', 'taxa'))) %>% 
  mutate(res = str_replace(res, '^.+//',''),
         res = str_replace(res, '_lefse.+$',''))  %>% 
  rename(grp = res) %>% 
  mutate(grp = str_replace(grp, 'pull_','pull\\.')) %>% 
  separate(grp, into = c('cohort','outcome'), sep = '\\.')

@@

>>>>

res_all <- res %>% 
  set_names(res) %>% 
  map(~ read_tsv(., col_names = c('feature','xx','direction','score','pval')) %>% 
        filter(!is.na(score))) %>% 
  keep(~ nrow(.) > 0) %>% 
  bind_rows(.id = 'res') %>% 
  mutate(tbl = if_else(str_detect(res, 'pcts'), 'pathway', 'taxa')) %>% 
  mutate(res = str_replace(res, '^.+//',''),
         res = str_replace(res, '_lefse.+$',''))  %>% 
  rename(grp = res) %>% 
  mutate(grp = str_replace(grp, 'pull_','pull\\.')) %>% 
  separate(grp, into = c('cohort','outcome'), sep = '\\.')

@@

res_all %>% 
  write_csv('../data/shotgun_output/lefse_sig_results_taxa_and_pw.csv')
